GEO 365N/384S Seismic Data Processing \\ Final Project

### 2018-05-09 paper.tex
update

\plot{vscan}{width=0.8\textwidth}{Velocity analysis for CMP 1280.}
\plot{nmo1}{width=0.8\textwidth}{NMO for CMP 1280.}

@@

>>>>

\plot{cmp1}{width=0.8\textwidth}{CMP 1280.}
\plot{vscan}{width=0.8\textwidth}{Velocity analysis for CMP 1280.}
\plot{nmo1}{width=0.8\textwidth}{CMP 1280 after NMO.}

\item We applied the same procedure with all CMP gathers. NMO velocity (Figure~\ref{fig:picks}) was picked using semblance scan. The events were flatten (Figure~\ref{fig:nmos}). We then stacked all the CMP gathers (Figure~\ref{fig:stack}). Our stack result does not resemble the published stacked data, which is actually a stacked and migrated file.

\plot{picks}{width=0.8\textwidth}{NMO velocity.}
\plot{nmos}{width=0.8\textwidth}{CMP gathers after NMO.}
\multiplot{2}{stack,stack-shot}{width=0.8\textwidth}{(a) Stacked data. (b) Published stacked data.}

\item We also tried DMO to correct for dips. We created a constant-velocity stack with 60 velocities starting from 1400 m/s and spacing interval of 20 m/s (Figure~\ref{fig:stacks}). We applied Fowler's method to transform the stack volume into the frequency-wavenumber domain and apply the velocity mapping (Figure~\ref{fig:map}). The result after applying Fowler's method is Figure~\ref{fig:dmo}. We then picked the DMO-corrected velocity automatically from the envelope (Figure~\ref{fig:vpick}). After the velocity was picked, we generated a DMO stack by slicing through the veolocity cube (Figure~\ref{fig:slice}). We examined CMP 380 to evaluate the velocity picking and to observe the change brought by DMO (Figure~\ref{fig:envelope}).

\plot{stacks}{width=0.8\textwidth}{NMO stack with an ensemble of constant velocities.}
\sideplot{map}{width=\textwidth}{Fourier-domain velocity map used in Fowler's DMO method.}
\plot{dmo}{width=0.8\textwidth}{Nankai dataset after DMO stacking with an ensemble of constant velocities.}
\plot{vpick}{width=0.8\textwidth}{Migration velocity picked automatically from DMO stacks.}
\plot{slice}{width=0.8\textwidth}{DMO stack generated by slicing the constant-velocity stacks.}
\sideplot{envelope}{width=\textwidth}{Comparison of velocity analysis before and after DMO at a selected CMP location.}

@@

\section{Migration}
